---
title: "Analysis Applied"
author: "Lewis Zou"
date: "11/28/2019"
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(fs)
library(gt)
library(tidymodels)
library(tidyverse)

worlds_16 <- readRDS("clean-data/worlds_2016.rds") %>%
  filter(position == "Team")
worlds_17 <- readRDS("clean-data/worlds_2017.rds") %>%
  filter(position == "Team")
worlds_18 <- readRDS("clean-data/worlds_2018.rds") %>%
  filter(position == "Team")
worlds_19 <- readRDS("clean-data/worlds_2019.rds") %>%
  filter(position == "Team")
```

# Creating the Model

We aim to create a model that can potential predict the results of games. Often, analysts declare that gold is a major reason for a victory or loss. They emphasize the importance of gold difference early on — however, from our analysis, we have found that gold difference fails to show a major impact. We now create two models; one that predicts based off gold difference at 10 and 15 minutes, and another that predicts based on dragons and barons killed.

<!-- Result ~ Gdat10 + Gdat15 -->

```{r model 2016 gg}
x_16_gg <- worlds_16 %>% 
  mutate(result = ifelse(result == 1, "Yes", "No")) %>%
  mutate(result = as.factor(result)) %>%
  mutate(prediction = predict(glm(data = worlds_16, result ~ gdat10 + gdat15, family = "binomial"), type = "response")) %>% 
  mutate(pred_result = as.factor(ifelse(prediction > mean(prediction), "Yes", "No"))) %>%
  metrics(truth = result, estimate = pred_result) %>%
  gt() %>%
  fmt_number(columns = vars(.estimate), 
             decimals = 3) %>%
  tab_header(title= "Predictions using Gold Difference",
             subtitle = "Gold Diff at 10 and 15 Minutes")
  
x_17_gg <- 
  worlds_17 %>% 
  mutate(result = ifelse(result == 1, "Yes", "No")) %>%
  mutate(result = as.factor(result)) %>%
  mutate(prediction = predict(glm(data = worlds_17, result ~ gdat10 + gdat15, family = "binomial"), type = "response")) %>% 
  mutate(pred_result = as.factor(ifelse(prediction > mean(prediction), "Yes", "No"))) %>%
  metrics(truth = result, estimate = pred_result) %>%
  gt()

x_18_gg <- 
  worlds_18 %>% 
  mutate(result = ifelse(result == 1, "Yes", "No")) %>%
  mutate(result = as.factor(result)) %>%
  mutate(prediction = predict(glm(data = worlds_18, result ~ gdat10 + gdat15, family = "binomial"), type = "response")) %>% 
  mutate(pred_result = as.factor(ifelse(prediction > mean(prediction), "Yes", "No"))) %>% 
  metrics(truth = result, estimate = pred_result) %>%
  gt()

x_19_gg <- 
  worlds_19 %>% 
  mutate(result = ifelse(result == 1, "Yes", "No")) %>%
  mutate(result = as.factor(result)) %>%
  mutate(prediction = predict(glm(data = worlds_19, result ~ gdat10 + gdat15, family = "binomial"), type = "response")) %>% 
  mutate(pred_result = as.factor(ifelse(prediction > mean(prediction), "Yes", "No"))) %>%
  metrics(truth = result, estimate = pred_result) %>%
  gt() 

saveRDS(x_16_gg, "graphics/model_gg_16.rds")
saveRDS(x_17_gg, "graphics/model_gg_17.rds")
saveRDS(x_18_gg, "graphics/model_gg_18.rds")
saveRDS(x_19_gg, "graphics/model_gg_19.rds")
```

<!-- Result ~ Dragons + Barons -->

```{r model 2016 db}
x_16_db <- 
  worlds_16 %>% 
  mutate(result = ifelse(result == 1, "Yes", "No")) %>%
  mutate(result = as.factor(result)) %>%
  mutate(prediction = predict(glm(data = worlds_16, result ~ teamdragkills + teambaronkills, family = "binomial"), type = "response")) %>% 
  mutate(pred_result = as.factor(ifelse(prediction > mean(prediction), "Yes", "No"))) %>%
  metrics(truth = result, estimate = pred_result) %>%
  gt() 

x_17_db <- 
  worlds_17 %>% 
  mutate(result = ifelse(result == 1, "Yes", "No")) %>%
  mutate(result = as.factor(result)) %>%
  mutate(prediction = predict(glm(data = worlds_17, result ~ teamdragkills + teambaronkills, family = "binomial"), type = "response")) %>% 
  mutate(pred_result = as.factor(ifelse(prediction > mean(prediction), "Yes", "No"))) %>%
  metrics(truth = result, estimate = pred_result) %>%
  gt() 

x_18_db <- 
  worlds_18 %>% 
  mutate(result = ifelse(result == 1, "Yes", "No")) %>%
  mutate(result = as.factor(result)) %>%
  mutate(prediction = predict(glm(data = worlds_18, result ~ teamdragkills + teambaronkills, family = "binomial"), type = "response")) %>% 
  mutate(pred_result = as.factor(ifelse(prediction > mean(prediction), "Yes", "No"))) %>%
  metrics(truth = result, estimate = pred_result) %>%
  gt() 

x_19_db <- 
  worlds_19 %>% 
  mutate(result = ifelse(result == 1, "Yes", "No")) %>%
  mutate(result = as.factor(result)) %>%
  mutate(prediction = predict(glm(data = worlds_19, result ~ teamdragkills + teambaronkills, family = "binomial"), type = "response")) %>% 
  mutate(pred_result = as.factor(ifelse(prediction > mean(prediction), "Yes", "No"))) %>%
  metrics(truth = result, estimate = pred_result) %>%
  gt()

saveRDS(x_16_db, "graphics/model_db_16.rds")
saveRDS(x_17_db, "graphics/model_db_17.rds")
saveRDS(x_18_db, "graphics/model_db_18.rds")
saveRDS(x_19_db, "graphics/model_db_19.rds")
```


<!-- Other --> 

```{r}
wins_tg_2016 <-
  worlds_16 %>%
  group_by(team) %>%
  summarize(wins = sum(result), 
            total = length(team), 
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, wins)) + 
  geom_point(color = "black") + 
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  labs(title = "Wins as a result of Gold",
       subtitle = "2016",
       x = "Gold per Game",
       y = "Wins")

wins_tg_2017 <- 
  worlds_17 %>%
  group_by(team) %>%
  summarize(wins = sum(result), 
            total = length(team), 
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, wins)) + 
  geom_point(color = "black") + 
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  labs(title = "Wins as a result of Gold",
       subtitle = "2017",
       x = "Gold per Game",
       y = "Wins")

wins_tg_2018 <- 
  worlds_18 %>%
  group_by(team) %>%
  summarize(wins = sum(result), 
            total = length(team), 
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, wins)) + 
  geom_point(color = "black") + 
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  labs(title = "Wins as a result of Gold",
       subtitle = "2018",
       x = "Gold per Game",
       y = "Wins")

wins_tg_2019 <- 
  worlds_19 %>%
  group_by(team) %>%
  summarize(wins = sum(result), 
            total = length(team), 
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, wins)) + 
  geom_point(color = "black") + 
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  labs(title = "Wins as a result of Gold",
       subtitle = "2019",
       x = "Gold per Game",
       y = "Wins")

saveRDS(wins_tg_2016, "graphics/wins_tg_2016.rds")
saveRDS(wins_tg_2017, "graphics/wins_tg_2017.rds")
saveRDS(wins_tg_2018, "graphics/wins_tg_2018.rds")
saveRDS(wins_tg_2019, "graphics/wins_tg_2019.rds")
```

```{r Graph of Dragons per Game vs Gold per Game}

# Everything here was generally the same.
# I summarized by wins, total occurances, and total dragons to get it on per game basis.
# I graphed dragons against wins and labeled everything accordingly.

dragons_tg_2016 <-
  worlds_16 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            total_dragons = sum(teamdragkills) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, total_dragons)) + 
  geom_point(color = "darkblue") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkblue") +
  labs(title = "Dragons as a result of Gold",
       subtitle = "2016",
       x = "Gold per Game",
       y = "Dragons per Game")

dragons_tg_2017 <- 
  worlds_17 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            total_dragons = sum(teamdragkills) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, total_dragons)) +  
  geom_point(color = "darkblue") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkblue") +
  labs(title = "Dragons as a result of Gold",
       subtitle = "2017",
       x = "Gold per Game",
       y = "Dragons per Game")

dragons_tg_2018 <- worlds_18 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            total_dragons = sum(teamdragkills) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, total_dragons)) + 
  geom_point(color = "darkblue") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkblue") +
  labs(title = "Dragons as a result of Gold",
       subtitle = "2018",
       x = "Gold per Game",
       y = "Dragons per Game")

dragons_tg_2019 <- worlds_19 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            total_dragons = sum(teamdragkills) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, total_dragons)) + 
  geom_point(color = "darkblue") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkblue") +
  labs(title = "Dragons as a result of Gold",
       subtitle = "2019",
       x = "Gold per Game",
       y = "Dragons per Game")

saveRDS(dragons_tg_2016, "graphics/dragons_tg_2016.rds")
saveRDS(dragons_tg_2017, "graphics/dragons_tg_2017.rds")
saveRDS(dragons_tg_2018, "graphics/dragons_tg_2018.rds")
saveRDS(dragons_tg_2019, "graphics/dragons_tg_2019.rds")
```

```{r Graph of Barons per Game vs Gold per Game}

# Everything here was generally the same.
# I summarized by wins, total occurances, and total barons to get it on per game basis.
# I graphed barons against wins and labeled everything accordingly.

barons_tg_2016 <-
  worlds_16 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            total_barons = sum(teambaronkills) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, total_barons)) + 
  geom_point(color = "darkcyan") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkcyan") +
  labs(title = "Barons as a result of Gold",
       subtitle = "2016",
       x = "Gold per Game",
       y = "Barons per Game")

barons_tg_2017 <- 
  worlds_17 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            total_barons = sum(teambaronkills) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, total_barons)) +  
  geom_point(color = "darkcyan") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkcyan") +
  labs(title = "Barons as a result of Gold",
       subtitle = "2017",
       x = "Gold per Game",
       y = "Barons per Game")

barons_tg_2018 <- 
  worlds_18 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            total_barons = sum(teambaronkills) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, total_barons)) + 
  geom_point(color = "darkcyan") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkcyan") +
  labs(title = "Barons as a result of Gold",
       subtitle = "2018",
       x = "Gold per Game",
       y = "Barons per Game")

barons_tg_2019 <- 
  worlds_19 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            total_barons = sum(teambaronkills) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, total_barons)) + 
  geom_point(color = "darkcyan") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkcyan") +
  labs(title = "Barons as a result of Gold",
       subtitle = "2019",
       x = "Gold per Game",
       y = "Barons per Game")

saveRDS(barons_tg_2016, "graphics/barons_tg_2016.rds")
saveRDS(barons_tg_2017, "graphics/barons_tg_2017.rds")
saveRDS(barons_tg_2018, "graphics/barons_tg_2018.rds")
saveRDS(barons_tg_2019, "graphics/barons_tg_2019.rds")
```

```{r Graph of Wards per Game vs Gold per Game}

# Everything here was generally the same.
# I summarized by wins, total occurances, and total wards to get it on per game basis.
# I graphed wards against wins and labeled everything accordingly.

wards_tg_2016 <-
  worlds_16 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            wards = sum(wards) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, wards)) + 
  geom_point(color = "darkturquoise") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkturquoise") +
  labs(title = "Wards as a result of Gold",
       subtitle = "2016",
       x = "Gold per Game",
       y = "Wards per Game")

wards_tg_2017 <- 
  worlds_17 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            wards = sum(wards) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, wards)) +  
  geom_point(color = "darkturquoise") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkturquoise") +
  labs(title = "Wards as a result of Gold",
       subtitle = "2017",
       x = "Gold per Game",
       y = "Wards per Game")

wards_tg_2018 <- 
  worlds_18 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            wards = sum(wards) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, wards)) + 
  geom_point(color = "darkturquoise") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkturquoise") +
  labs(title = "Wards as a result of Gold",
       subtitle = "2018",
       x = "Gold per Game",
       y = "Wards per Game")

wards_tg_2019 <- 
  worlds_19 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            wards = sum(wards) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, wards)) + 
  geom_point(color = "darkturquoise") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkturquoise") +
  labs(title = "Wards as a result of Gold",
       subtitle = "2019",
       x = "Gold per Game",
       y = "Wards per Game")

saveRDS(wards_tg_2016, "graphics/wards_tg_2016.rds")
saveRDS(wards_tg_2017, "graphics/wards_tg_2017.rds")
saveRDS(wards_tg_2018, "graphics/wards_tg_2018.rds")
saveRDS(wards_tg_2019, "graphics/wards_tg_2019.rds")
```
