---
title: "Analysis Applied"
author: "Lewis Zou"
date: "11/28/2019"
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(fs)
library(gt)
library(tidymodels)
library(tidyverse)

worlds_16 <- readRDS("clean-data/worlds_2016.rds") %>%
  filter(position == "Team")
worlds_17 <- readRDS("clean-data/worlds_2017.rds") %>%
  filter(position == "Team")
worlds_18 <- readRDS("clean-data/worlds_2018.rds") %>%
  filter(position == "Team")
worlds_19 <- readRDS("clean-data/worlds_2019.rds") %>%
  filter(position == "Team")

# In here I loaded the necessary packages and dataset.
```

# Creating the Model

We aimed to create a model that can potential predict the results of games. Often, analysts declare that gold is a major reason for a victory or loss. They emphasize the importance of gold difference early on — however, from our analysis, we have found that gold difference fails to show a major impact. Instead, we found that the number of dragons and barons that teams captured increased their chances of winning even more. While gold remains important in thriving in the game, the actual gold difference in the early game before dragons and barons are taken is too minimal to create a major separation. We now create two models; one that predicts based off gold difference at 10 and 15 minutes, and another that predicts based on dragons and barons killed. 

Note: Our model is basic and many errors may have occured. For one, we used the regression to predict the results of games in the 2016 - 2019 LoL World Championships. The accuracy number reflects the proportion of guesses that were correct, while the kap (kappa) number reflects how much better the model did than randomly guessing.

We wanted to see how the impact of these factors changed over the years. It is clear that, as we had initially found earlier in the project, that the model using dragon and baron statistics were much more accurate than the one using gold difference.

We also wanted to show the correlation between significant factors and gold. It's clear that although gold may not directly impact the outcome of the game as we had thought, it still is important in helping capture the objectives that are necessary for victory. We provided a slider that would allow scrolling through the years, and graphs relating gold to wins, dragons, barons, and wards (for sight on the map). We provide our full conclusions in the 'Conclusion' tab. 

<!-- Result ~ Gdat10 + Gdat15 -->

```{r models gg}

# I create an ifelse that would better compare the predictions with the result.
# I made both the result and prediction as factors.
# I create prediction using predict as a logistic model, and then used metrics to comapre the two.
# I repeated this with the four different years.

x_16_gg <- 
  worlds_16 %>% 
  mutate(result = ifelse(result == 1, "Yes", "No")) %>%
  mutate(result = as.factor(result)) %>%
  mutate(prediction = predict(glm(data = worlds_16, result ~ gdat10 + gdat15, family = "binomial"), type = "response")) %>% 
  mutate(pred_result = as.factor(ifelse(prediction > mean(prediction), "Yes", "No"))) %>%
  metrics(truth = result, estimate = pred_result) %>%
  gt() %>%
  fmt_number(columns = vars(.estimate), 
             decimals = 3) %>%
  tab_header(title= "Predictions using Gold Difference",
             subtitle = "Gold Diff at 10 and 15 Minutes")
  
x_17_gg <- 
  worlds_17 %>% 
  mutate(result = ifelse(result == 1, "Yes", "No")) %>%
  mutate(result = as.factor(result)) %>%
  mutate(prediction = predict(glm(data = worlds_17, result ~ gdat10 + gdat15, family = "binomial"), type = "response")) %>% 
  mutate(pred_result = as.factor(ifelse(prediction > mean(prediction), "Yes", "No"))) %>%
  metrics(truth = result, estimate = pred_result) %>%
  gt()

x_18_gg <- 
  worlds_18 %>% 
  mutate(result = ifelse(result == 1, "Yes", "No")) %>%
  mutate(result = as.factor(result)) %>%
  mutate(prediction = predict(glm(data = worlds_18, result ~ gdat10 + gdat15, family = "binomial"), type = "response")) %>% 
  mutate(pred_result = as.factor(ifelse(prediction > mean(prediction), "Yes", "No"))) %>% 
  metrics(truth = result, estimate = pred_result) %>%
  gt()

x_19_gg <- 
  worlds_19 %>% 
  mutate(result = ifelse(result == 1, "Yes", "No")) %>%
  mutate(result = as.factor(result)) %>%
  mutate(prediction = predict(glm(data = worlds_19, result ~ gdat10 + gdat15, family = "binomial"), type = "response")) %>% 
  mutate(pred_result = as.factor(ifelse(prediction > mean(prediction), "Yes", "No"))) %>%
  metrics(truth = result, estimate = pred_result) %>%
  gt() 

# I used saveRDS to save the models as objects.

saveRDS(x_16_gg, "graphics/model_gg_16.rds")
saveRDS(x_17_gg, "graphics/model_gg_17.rds")
saveRDS(x_18_gg, "graphics/model_gg_18.rds")
saveRDS(x_19_gg, "graphics/model_gg_19.rds")

```

<!-- Result ~ Dragons + Barons -->

```{r models db}

# I used a similar process as previously.
# However, instead of using gdat10 + gdat15, I used teamdragkills and teambaronkills

x_16_db <- 
  worlds_16 %>% 
  mutate(result = ifelse(result == 1, "Yes", "No")) %>%
  mutate(result = as.factor(result)) %>%
  mutate(prediction = predict(glm(data = worlds_16, result ~ teamdragkills + teambaronkills, family = "binomial"), type = "response")) %>% 
  mutate(pred_result = as.factor(ifelse(prediction > mean(prediction), "Yes", "No"))) %>%
  metrics(truth = result, estimate = pred_result) %>%
  gt() 

x_17_db <- 
  worlds_17 %>% 
  mutate(result = ifelse(result == 1, "Yes", "No")) %>%
  mutate(result = as.factor(result)) %>%
  mutate(prediction = predict(glm(data = worlds_17, result ~ teamdragkills + teambaronkills, family = "binomial"), type = "response")) %>% 
  mutate(pred_result = as.factor(ifelse(prediction > mean(prediction), "Yes", "No"))) %>%
  metrics(truth = result, estimate = pred_result) %>%
  gt() 

x_18_db <- 
  worlds_18 %>% 
  mutate(result = ifelse(result == 1, "Yes", "No")) %>%
  mutate(result = as.factor(result)) %>%
  mutate(prediction = predict(glm(data = worlds_18, result ~ teamdragkills + teambaronkills, family = "binomial"), type = "response")) %>% 
  mutate(pred_result = as.factor(ifelse(prediction > mean(prediction), "Yes", "No"))) %>%
  metrics(truth = result, estimate = pred_result) %>%
  gt() 

x_19_db <- 
  worlds_19 %>% 
  mutate(result = ifelse(result == 1, "Yes", "No")) %>%
  mutate(result = as.factor(result)) %>%
  mutate(prediction = predict(glm(data = worlds_19, result ~ teamdragkills + teambaronkills, family = "binomial"), type = "response")) %>% 
  mutate(pred_result = as.factor(ifelse(prediction > mean(prediction), "Yes", "No"))) %>%
  metrics(truth = result, estimate = pred_result) %>%
  gt()

# I used saveRDS to save the models as objects.

saveRDS(x_16_db, "graphics/model_db_16.rds")
saveRDS(x_17_db, "graphics/model_db_17.rds")
saveRDS(x_18_db, "graphics/model_db_18.rds")
saveRDS(x_19_db, "graphics/model_db_19.rds")
```

<!-- Other --> 

```{r wins as a result of object}

# I grouped by team, and then used summarize to get the wins, and totalgold per game.
# I used ggplot and labeled the graphs accordingly.
# I repeated this for the different years, and saved it as rds objects.

wins_tg_2016 <-
  worlds_16 %>%
  group_by(team) %>%
  summarize(wins = sum(result), 
            total = length(team), 
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, wins)) + 
  geom_point(color = "black") + 
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  labs(title = "Wins as a result of Gold",
       subtitle = "2016",
       x = "Gold per Game",
       y = "Wins")

wins_tg_2017 <- 
  worlds_17 %>%
  group_by(team) %>%
  summarize(wins = sum(result), 
            total = length(team), 
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, wins)) + 
  geom_point(color = "black") + 
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  labs(title = "Wins as a result of Gold",
       subtitle = "2017",
       x = "Gold per Game",
       y = "Wins")

wins_tg_2018 <- 
  worlds_18 %>%
  group_by(team) %>%
  summarize(wins = sum(result), 
            total = length(team), 
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, wins)) + 
  geom_point(color = "black") + 
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  labs(title = "Wins as a result of Gold",
       subtitle = "2018",
       x = "Gold per Game",
       y = "Wins")

wins_tg_2019 <- 
  worlds_19 %>%
  group_by(team) %>%
  summarize(wins = sum(result), 
            total = length(team), 
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, wins)) + 
  geom_point(color = "black") + 
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  labs(title = "Wins as a result of Gold",
       subtitle = "2019",
       x = "Gold per Game",
       y = "Wins")

saveRDS(wins_tg_2016, "graphics/wins_tg_2016.rds")
saveRDS(wins_tg_2017, "graphics/wins_tg_2017.rds")
saveRDS(wins_tg_2018, "graphics/wins_tg_2018.rds")
saveRDS(wins_tg_2019, "graphics/wins_tg_2019.rds")
```

```{r Graph of Dragons per Game vs Gold per Game}

# Everything here was generally the same.
# I summarized by wins, total occurances, and total dragons to get it on per game basis.
# I graphed dragons against gold and labeled everything accordingly.

dragons_tg_2016 <-
  worlds_16 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            total_dragons = sum(teamdragkills) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, total_dragons)) + 
  geom_point(color = "darkblue") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkblue") +
  labs(title = "Dragons as a result of Gold",
       subtitle = "2016",
       x = "Gold per Game",
       y = "Dragons per Game")

dragons_tg_2017 <- 
  worlds_17 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            total_dragons = sum(teamdragkills) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, total_dragons)) +  
  geom_point(color = "darkblue") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkblue") +
  labs(title = "Dragons as a result of Gold",
       subtitle = "2017",
       x = "Gold per Game",
       y = "Dragons per Game")

dragons_tg_2018 <- worlds_18 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            total_dragons = sum(teamdragkills) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, total_dragons)) + 
  geom_point(color = "darkblue") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkblue") +
  labs(title = "Dragons as a result of Gold",
       subtitle = "2018",
       x = "Gold per Game",
       y = "Dragons per Game")

dragons_tg_2019 <- worlds_19 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            total_dragons = sum(teamdragkills) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, total_dragons)) + 
  geom_point(color = "darkblue") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkblue") +
  labs(title = "Dragons as a result of Gold",
       subtitle = "2019",
       x = "Gold per Game",
       y = "Dragons per Game")

saveRDS(dragons_tg_2016, "graphics/dragons_tg_2016.rds")
saveRDS(dragons_tg_2017, "graphics/dragons_tg_2017.rds")
saveRDS(dragons_tg_2018, "graphics/dragons_tg_2018.rds")
saveRDS(dragons_tg_2019, "graphics/dragons_tg_2019.rds")
```

```{r Graph of Barons per Game vs Gold per Game}

# Everything here was generally the same.
# I summarized by wins, total occurances, and total barons to get it on per game basis.
# I graphed barons against gold and labeled everything accordingly.

barons_tg_2016 <-
  worlds_16 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            total_barons = sum(teambaronkills) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, total_barons)) + 
  geom_point(color = "darkcyan") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkcyan") +
  labs(title = "Barons as a result of Gold",
       subtitle = "2016",
       x = "Gold per Game",
       y = "Barons per Game")

barons_tg_2017 <- 
  worlds_17 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            total_barons = sum(teambaronkills) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, total_barons)) +  
  geom_point(color = "darkcyan") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkcyan") +
  labs(title = "Barons as a result of Gold",
       subtitle = "2017",
       x = "Gold per Game",
       y = "Barons per Game")

barons_tg_2018 <- 
  worlds_18 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            total_barons = sum(teambaronkills) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, total_barons)) + 
  geom_point(color = "darkcyan") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkcyan") +
  labs(title = "Barons as a result of Gold",
       subtitle = "2018",
       x = "Gold per Game",
       y = "Barons per Game")

barons_tg_2019 <- 
  worlds_19 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            total_barons = sum(teambaronkills) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, total_barons)) + 
  geom_point(color = "darkcyan") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkcyan") +
  labs(title = "Barons as a result of Gold",
       subtitle = "2019",
       x = "Gold per Game",
       y = "Barons per Game")

saveRDS(barons_tg_2016, "graphics/barons_tg_2016.rds")
saveRDS(barons_tg_2017, "graphics/barons_tg_2017.rds")
saveRDS(barons_tg_2018, "graphics/barons_tg_2018.rds")
saveRDS(barons_tg_2019, "graphics/barons_tg_2019.rds")
```

```{r Graph of Wards per Game vs Gold per Game}

# Everything here was generally the same.
# I summarized by wins, total occurances, and total wards to get it on per game basis.
# I graphed wards against gold and labeled everything accordingly.

wards_tg_2016 <-
  worlds_16 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            wards = sum(wards) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, wards)) + 
  geom_point(color = "darkturquoise") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkturquoise") +
  labs(title = "Wards as a result of Gold",
       subtitle = "2016",
       x = "Gold per Game",
       y = "Wards per Game")

wards_tg_2017 <- 
  worlds_17 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            wards = sum(wards) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, wards)) +  
  geom_point(color = "darkturquoise") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkturquoise") +
  labs(title = "Wards as a result of Gold",
       subtitle = "2017",
       x = "Gold per Game",
       y = "Wards per Game")

wards_tg_2018 <- 
  worlds_18 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            wards = sum(wards) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, wards)) + 
  geom_point(color = "darkturquoise") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkturquoise") +
  labs(title = "Wards as a result of Gold",
       subtitle = "2018",
       x = "Gold per Game",
       y = "Wards per Game")

wards_tg_2019 <- 
  worlds_19 %>%
  group_by(team) %>%
  summarize(total = length(team), 
            wards = sum(wards) / total,
            totalgold = sum(totalgold) / total) %>%
  ggplot(aes(totalgold, wards)) + 
  geom_point(color = "darkturquoise") + 
  geom_smooth(method = "lm", se = FALSE, color = "darkturquoise") +
  labs(title = "Wards as a result of Gold",
       subtitle = "2019",
       x = "Gold per Game",
       y = "Wards per Game")

saveRDS(wards_tg_2016, "graphics/wards_tg_2016.rds")
saveRDS(wards_tg_2017, "graphics/wards_tg_2017.rds")
saveRDS(wards_tg_2018, "graphics/wards_tg_2018.rds")
saveRDS(wards_tg_2019, "graphics/wards_tg_2019.rds")
```
